Alternative Methods for Implementing Explicit and Finding Implicit Sharing in embedded DSLs

### 2022-12-14 paper/paper.tex
plotting addchains hashconsing scaling example

Implicit sharing via hash-consing prevents duplication in the resulting DAG, but
unfortunately doesn't prevent redundant computation. Consider the following
equivalent attempt at using Haskell's built-in sharing in the finally tagless DSL
\begin{minted}{haskell}
redundant :: Exp Graph -> Exp Graph -> Exp Graph
redundant x y =
  let
    z = add x y
  in add z z
\end{minted}
Note {\bf z} is a wrapper around a State monad. Recall the implementation of
{\bf add} via hash consing
\begin{minted}{haskell}
add e1 e2 = Graph (do
                   h1 <- unGraph e1
                   h2 <- unGraph e2
                   hashcons $ NAdd h1 h2)
\end{minted}
In order to

>>>>

Implicit sharing via hash-consing prevents duplication in the resulting DAG, but
unfortunately doesn't prevent redundant computation. Consider the following
equivalent attempt at using Haskell's built-in sharing in the finally tagless DSL
\begin{minted}{haskell}
dslSharing :: Exp Graph -> Exp Graph -> Exp Graph
dslSharing x y =
  let
    z = add x y
  in add z z
\end{minted}
Note {\bf z} is a wrapper around a State monad. Recall the implementation of
{\bf add} via hash consing
\begin{minted}{haskell}
add e1 e2 = Graph (do
                   h1 <- unGraph e1
                   h2 <- unGraph e2
                   hashcons $ NAdd h1 h2)
\end{minted}
The values {\bf h1} and {\bf h2} need to be explicitely evaluated through the
State monad, meaning even if {\bf e1} and {\bf e2} are the same shared Haskell
value, their underlying computations will be performed twice. Hash-consing will
prevent these redundencies from appearing in the resulting DAG, the the entire
unshared AST wil still be traversed, performing a hash-cons on each node.
